Viability of FTIR on fossil pollen

### 2020-02-11 manuscript.Rmd
minor changes after meeting with Al

Research Questions:
1. chemical variation between taxa in the same cores.
2. chemical variation between taxa between cores 
3. chemical variation of pollen with depths/age
## Cores
Dalman Lado:

Totenmoos [@heissUltenValleySouth2005]:
- bog-sediment core
- min 1000 grains counted
- Picea, Pinus very common, switch at 10000 BP from Pinus to Picea
- Alnus, Betula throughout
- Abies, Fagus after 9000 BP
- trace Quercus

@@

@@

Anywhere from 18 to 30 samples is reasonable.
At 3 cores 5 taxa:
Minimum 4 samples per core 
Maximum 9 samples per core
```{r}
print('No. of samples at Three Cores')
signif(M/3, 3)
```
At 2 cores 5 taxa:
Minimum 7 samples per core
Maximum 14 samples per core
```{r}
print('No. of samples at Two Cores')
signif(M/2, 3)
```

>>>>

Research Questions:
1. chemical variation between taxa in the same cores.
2. chemical variation between taxa between cores 
3. chemical variation of pollen with depths/age
## Cores
Dalmuttlado:
- pine
- holocene

Totenmoos [@heissUltenValleySouth2005]:
- bog-sediment core; past 15000 yrs
- min 1000 grains counted
- Picea, Pinus very common, switch at 10000 BP from Pinus to Picea
- Alnus, Betula throughout
- Abies, Fagus after 9000 BP
- trace Quercus

@@

Tiefer See:
- 1870-2010
- laminated sediments
- Pinus pollen

@@

Anywhere from 18 to 30 samples is reasonable.
At 3 cores 5 taxa:
Minimum 4 samples per core 
Maximum 9 samples per core

```{r}
print('No. of samples at Three Cores')
signif(M/3, 3)
```
At 2 cores 5 taxa:
Minimum 7 samples per core
Maximum 14 samples per core

```{r}
print('No. of samples at Two Cores')
signif(M/2, 3)
```
